Simple connectome inference from partial\\[1ex] correlation statistics in calcium imaging

### 2014-09-08 oral/slides.tex
slides

@@

@@

But this problem is \textbf{difficult} because of...

\begin{tabular*}{\textwidth}{l r} \hline
&\multirow{3}{*}{\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}}\\

{\color{red} \textbf{masking} effects}
& \\ 
& \\
\end{tabular}

% \begin{itemize}
% \item {\color{red} \textbf{masking} effects},
% \includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}
% \item {\color{red} \textbf{low} sampling rate},
% \includegraphics[width=4cm]{images/slowsamplingrate.png}
% \item {\color{red} \textbf{slow} decay} of fluorescence.
% \includegraphics[width=4cm]{images/original_curve_gr}
% \end{itemize}

>>>>

\usepackage{textpos}

@@

\note{

	Before the main part of this presentation, I would like to mention that we are not biologist and we are not expert of the connectome inference. We see the challenge as an inference problem and maybe in a naive point of view for some points.

}

@@

\vspace{-100pt}
But this problem is \textbf{difficult} because of...

\begin{textblo}
\begin{minipage}{0.95\linewidth}
{\color{red} \textbf{masking} effects}
\end{minipage}

\begin{minipage}{0.95\linewidth}
{\color{red} \textbf{masking} effects}
\end{minipage}

% \begin{tabular*}{\textwidth}{l r} \hline
% &\multirow{3}{*}{\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}}\\

% {\color{red} \textbf{masking} effects}
% & \\ 
% & \\

% \item {\color{red} \textbf{masking} effects},
% \includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}
% \item {\color{red} \textbf{low} sampling rate},
% \includegraphics[width=4cm]{images/slowsamplingrate.png}
% \item {\color{red} \textbf{slow} decay} of fluorescence.
% \includegraphics[width=4cm]{images/original_curve_gr}
% \end{itemize}
